---
output:
  html_document: default
  word_document: default
---
#Regression Models Project Executive Summary
The goal of this study is to determine the difference in miles per gallon in
automatic versus manual transmission vehicles. To estimate this, we will use linear 
regression models. The overall conclusion is that we cannot definitevely say whether
the type of transmission affects MPG.

#Preprocesing and Data Exploration
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(corrplot)
library(car)
```
```{r}
data(mtcars)
dim(mtcars)
sum(is.na(mtcars))
```
The mtcars dataset has 32 observations and 11 variables. There is no missing data. Looking at the summary statistics (see appendix), 41% of the observations are vehicles with automatic transmissions. the average MPG is approximately 20 MPG. Further, we observe that automatic vehicles get more MPG (see appendix box plot). Finally, with mean > median MPG shows a right skew.

#Modeling, Model #1
```{r}
model <- lm(mpg ~ am, data = mtcars)
summary(model)
```
The first model built is a simple linear regression, with AM as the independent variable. The result indicates that automatic vehicles get 7.245 more MPG than manual transmission vehicles.  
#Modeling, Model #2
```{r}
model2 <- lm(log(mpg) ~ am + wt + cyl + hp, data = mtcars)
summary(model2)
vif(model2)
```
The second model uses am, wt, and hp as the independent variables and the dependent variable uses a natrual log to help address the right skew. Variable selection is based on the variables with the strongest covariance with MPG (see appendix). I chose to omit many to avoid multicollinearity. This model has an adj. r-squared of .8267 and shows that am is insignificant, and that only the wt variable is significant with a -16.4% change with each 1000 pound increase. The VIF doesn't indicate that multicollinearity is a concern. Finally, the fitted vs. residual plot (see appendix) shows a little evidence of heteroskedasticity. 

#Conclusion
After fitting two models, this study did not observe a statistically significant difference in MPG for automatic and manual transmissions. As such, one cannot quantify the difference. The best one could estimate is ~ +7 MPG for automatics, not controlling for other variables.

#Appendix
```{r}
#Summary Stats
summary(mtcars)

#Box Plot
ggplot(mtcars, aes(x = factor(am), y = mpg)) + geom_boxplot()

#Correlations
corrplot(cor(mtcars))

#Model 2 Plots
par(mfrow = c(2,2))
plot(model2)
```